Data tests

### 2022-07-27 Old/Shiny/Test/Data tests.Rmd
Spelling.
Maybe found the function.

testing
```

>>>>

testing
```
```{r}
?validate
```

```{r}
read_proff_names <- function(file, start, end) {
  # Specifying encoding to deal with occasional errors
  read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame") |>
    html_table() |>
    names()
}

read_proff_names("Data/Kreftforeningen.html", "2002")

nrk <- read_html("Data/NRK.html")
nrk_node <- nrk |> html_node("#inner-frame")

class(nrk_node)

wrong <- read_html("Data/Kreft_wrong.html") |> html_node("#inner-frame") |> html_table()

wrong

right <- read_html("Data/Kreftforeningen.html", encoding = "UTF-8") |>
    html_node("#inner-frame") |>
    html_table()

right

"REGNSKAPSPERIODE" %in% names(wrong)

if (class(nrk_node) == "xml_missing") {
  TRUE
} else {
  FALSE
}

read_proff_read <- function(file) {
  read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame")
}

testing <- read_html("Data/Kreftforeningen.html", encoding = "UTF-8") |>
    html_node("#inner-frame")

class(testing)

read_proff_table <- function(object) {
  html_table()
}

empty <- read_proff_read("Data/Kreft_wrong.html") |> html_table()

"REGNSKAPSPERIODE" %in% names(empty)

read_proff_testing(testing, "2002", "2021")

htmldata <- function(file, start, end) {
  node <- read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame")

  if (class(node) == "xml_node") {
    table <- node |> html_table()
  } else {
    message("Table error.")
  }

  if ("REGNSKAPSPERIODE" %in% names(table)) {
    if (as.character(all_of(start)) %in% names(table) &&
    as.character(all_of(end)) %in% names(table)) {
      read_proff_notest("Data/Kreftforeningen.html", start, end)
    } else {
      message("character error")
    }
  } else {
    message("Regnskap error.")
  }
}

htmldata("Data/Kreftforeningen.html", "2002", "2021")

weird <- read_html("Data/Kreftforeningen.html", encoding = "UTF-8") |> 
  html_element("#inner-frame") |> html_table()

names(weird)

"2002" %in% names(weird)

read_test <- function(object, start, end) {
  if (as.character(all_of(start)) %in% names(object) &&
    as.character(all_of(end)) %in% names(object)) {
    TRUE
  } else {
    FALSE
  }
}

html_first_test <- function(file) {

  htmltest <- read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame")

  if (class(htmltest) == "xml_node") {
    htmltable <- htmltest |> html_table()
  } else {
    "table error"
  }

  if ("REGNSKAPSPERIODE" %in% names(htmltable)) {
    htmlready <- htmltable
  } else {
    "regnskap error"
  }
}

html_first_test("Data/Kreftforeningen.html")

html_second_test <- function(object, start, end) {
  if (as.character(all_of(start)) %in% names(object) &&
    as.character(all_of(end)) %in% names(object)) {
    read_proff_notest(object, start, end)
  } else {
    FALSE
  }
}

html_second_test(htmlready, "2002", "2021")

read_test(weird, "2002", "2021")

html_testing <- function(file, start, end) {

  htmltest <- read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame")

  if (class(htmltest) == "xml_node") {
    htmltable <- htmltest |> html_table()
  } else {
    "table error"
  }

  if ("REGNSKAPSPERIODE" %in% names(htmltable)) {
    htmlready <- htmltable
  } else {
    "regnskap error"
  }

  if (as.character(all_of(start)) %in% names(htmlready) &&
    as.character(all_of(end)) %in% names(htmlready)) {
    read_proff_notest(file, start, end)
  } else {
    "year error"
  }
}

html_testing("Data/Kreftforeningen.html", "2002", "2021")

check

if (check == TRUE) {
  read_proff_notest("Data/Kreftforeningen.html", "2002", "2021")
} else {
  "what's wrong"
}
```

- test if html
- test if node is present
- test if correct table
- go for it

# Part 2 - version with integrated test
read_proff_complete <- function(object, start, end) {
  if (as.character(all_of(start)) %in% names(object) &&
    as.character(all_of(end)) %in% names(object)) {
    object |>
      # removing empty column, using all_of(argument)
      select(
        REGNSKAPSPERIODE:all_of(start)
      ) |>
      # removing white space
      mutate(
        REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
      ) |>
      # removing duplicate table sometimes created by read_html()
      filter(
        !row_number() > 176
      ) |>
      # removing duplicate rows
      filter(
        !grepl("Lukk", REGNSKAPSPERIODE)
      ) |>
      # tidying data using pivot_longer() and all_of(argument)
      pivot_longer(
        all_of(end):all_of(start),
        names_to = "year"
      ) |>
      # creating a currency code column and turning current currency codes into
      # NAs
      mutate(
        # changing to real NAs
        value = na_if(value, "-"),
        # turning years into numbers
        year = as.integer(year),
        # creating a currency code column and turning current currency codes into
        # NAs
        valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
      ) |>
      # filling the currency column
      fill(
        valutakode,
        .direction = "updown"
      ) |>
      # removing dates and redundant currency
      filter(
        REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
          REGNSKAPSPERIODE != "Valutakode"
      ) |>
      mutate(
        # removing white space in numbers
        value = str_replace_all(value, "\\s", ""),
        # turning numbers into true numbers
        value = as.numeric(value),
        # removing values that are years
        value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
      ) |>
      # removing any remaining duplicate rows
      distinct() |>
      # pivoting to create 'tidy' variables
      pivot_wider(
        names_from = REGNSKAPSPERIODE, values_from = value
      ) |>
      # tidying names
      clean_names() |>
      # removing headings from the table
      select(
        -lederlonn_i_hele_1000,
        -resultatregnskap_i_hele_1000,
        -balanseregnskap_i_hele_1000
      ) |>
      # making it clear what lonn refers to
      rename(
        lederlonn = lonn
      ) |>
      # Creating new variables for plots
      mutate(
        annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
        balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
      ) |>
      # arranging by year for practical display
      arrange(desc(year))
  } else {
    validate("Please ensure you have entered the correct start and end years")
  }
}

read_proff_notest <- function(file, start, end) {
  read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame") |>
    html_table() |> 
      # removing empty column, using all_of(argument)
      select(
        REGNSKAPSPERIODE:all_of(start)
      ) |>
      # removing white space
      mutate(
        REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
      ) |>
      # removing duplicate table sometimes created by read_html()
      filter(
        !row_number() > 176
      ) |>
      # removing duplicate rows
      filter(
        !grepl("Lukk", REGNSKAPSPERIODE)
      ) |>
      # tidying data using pivot_longer() and all_of(argument)
      pivot_longer(
        all_of(end):all_of(start),
        names_to = "year"
      ) |>
      # creating a currency code column and turning current currency codes into
      # NAs
      mutate(
        # changing to real NAs
        value = na_if(value, "-"),
        # turning years into numbers
        year = as.integer(year),
        # creating a currency code column and turning current currency codes into
        # NAs
        valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
      ) |>
      # filling the currency column
      fill(
        valutakode,
        .direction = "updown"
      ) |>
      # removing dates and redundant currency
      filter(
        REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
          REGNSKAPSPERIODE != "Valutakode"
      ) |>
      mutate(
        # removing white space in numbers
        value = str_replace_all(value, "\\s", ""),
        # turning numbers into true numbers
        value = as.numeric(value),
        # removing values that are years
        value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
      ) |>
      # removing any remaining duplicate rows
      distinct() |>
      # pivoting to create 'tidy' variables
      pivot_wider(
        names_from = REGNSKAPSPERIODE, values_from = value
      ) |>
      # tidying names
      clean_names() |>
      # removing headings from the table
      select(
        -lederlonn_i_hele_1000,
        -resultatregnskap_i_hele_1000,
        -balanseregnskap_i_hele_1000
      ) |>
      # making it clear what lonn refers to
      rename(
        lederlonn = lonn
      ) |>
      # Creating new variables for plots
      mutate(
        annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
        balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
      ) |>
      # arranging by year for practical display
      arrange(desc(year))
}
```

```{r}
# This may be the function =====================================================
```
